\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

\title{Paper Outline / Road Map }
\author{LIG - Verimag}

\begin{document}

\maketitle
\section{Abstract}
 we will keep it to the end. 

\section{Introduction}
\subsection{General intoduction} 

\begin{itemize}
  \item IEEE 802.15.4 overview (1 paragraph).
  \item TSCH Table Structure.
  \item 6top protocol and cell reservation.
\end{itemize}

 
\subsection{The project objectives and Results}

\begin{itemize}
  \item Randomity of cell selection in 6 top.
  \item Identifying the problem.(collision in the Dedicated cells of the TSCH tables between neighbor nodes)
  \item The suggested solution. (local mutual execlusion while reserving cells using 6top protocol)
\end{itemize}

\section{Background}
\subsection{6top cell reservation}
\begin{itemize}
  \item The rule of 6top.
  \item 2-step 6top Transaction
  \item 3-step 6top Transaction
  \item The communication of the cell reservation and deletion in the shared slot. 
  \end{itemize}
\subsection{filtering of the RX at the mac sublayer}
currently reading for This section \textbf{\textit{to be updated soon}}
\subsection{The concept of collision, hidden and exposed terminal.}
(collision only occurs at the reception)
\section{Proposed Mechanism}
\begin{itemize}
  \item The new created structure that will reserve the cells taken by the neighbors. 
  \item The use of the cell reservation Response to update the created structure.
  \item An schematics to explain the problem and the solution.
  \item Why we need to buffer the reserved cells , and how it's going to improve our approach. 
  \item The calculation of the buffer length. 
  \item The used value and why it fits the topologies.
  \end{itemize}
\section{Results}
\textbf{\textit{to be discussed with the supervisor, I will supply many options for the representions to choose the best fit for us}}
\section{Related Work}
\begin{itemize}
  \item The work done by Muraoka et al (the simulator creators), \textit{"6 Top Housekeeping"} 
  \item The work done by Phan Duy et al , a paper published in 22/03/2017 dealed with the same problem we are trying to solve.(I will supply you with the paper)
  \item Compariasno between Housekeeping and our approach.
  \end{itemize}  
\section{Conclusion}
  we will keep it to the end.


\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
Q.Wang, and X. Vilajosana, \emph{ 6top Protocol (6P). Internet Engineering Task Force, Tech. Rep. draft-ietf-6tisch-6top-protocol-00 } \hskip 1em plus
0.5em minus 0.4em\relax https://tools.ietf.org/html/draft-ietf-6tisch-6top-protocol-00 , April 2016.

\bibitem{IEEEhowto:kopka}
T. Watteyne et al, \emph{ Using IEEE 802.15.4e Time-Slotted Channel Hopping (TSCH) in the Internet of Things (IoT): Problem Statement } \hskip 1em plus
  0.5em minus 0.4em\relax https://tools.ietf.org/html/rfc7554 , May 2015.

\bibitem{IEEEhowto:kopka}
T. Winter et al, \emph{ RPL: IPv6 Routing Protocol for Low-Power and Lossy Networks } \hskip 1em plus
  0.5em minus 0.4em\relax https://tools.ietf.org/html/rfc6550 , March 2012.

\bibitem{IEEEhowto:kopka}
D. Dujovne et al, \emph{6tisch: deterministic ip-enabled industrial internet(of things)} \hskip 1em plus
  0.5em minus 0.4em\relax IEEE Communications Magazine — Communications Standards Supplement ,December 2014.
  
\bibitem{IEEEhowto:kopka}
J. Tripathi et al, \emph{A Performance Evaluation Study of RPL: Routing Protocol for Low Power and Lossy Networks} \hskip 1em plus
  0.5em minus 0.4em\relax  Information Sciences and Systems (CISS), 44th Annual Conference on (pp. 1-6). IEEE , March 2010.

\bibitem{IEEEhowto:kopka}
F. Theoleyre and G. Papadopoulos, \emph{Experimental Validation of a Distributed Self-Configured 6TiSCH with Traffic Isolation in Low Power Lossy Networks} \hskip 1em plus
  0.5em minus 0.4em\relax  Proceedings of the 19th ACM International Conference on Modeling, Analysis and Simulation of Wireless and Mobile Systems (pp. 102-110). ACM , November 2017.
  
\bibitem{IEEEhowto:kopka}
N. Accettura et al, \emph{A Decentralized Traffic Aware Scheduling in 6TiSCH Networks: Design and Experimental Evaluation} \hskip 1em plus
  0.5em minus 0.4em\relax   IEEE Internet of Things Journal, 2(6), 455-470 , December 2015.
  
\bibitem{IEEEhowto:kopka}
M. R. Palattella et al, \emph{On-the-Fly Bandwidth Reservation for 6TiSCH Wireless Industrial Networks} \hskip 1em plus
  0.5em minus 0.4em\relax  IEEE Sensors Journal, 16(2), 550-560,  September 2015.
  
\bibitem{IEEEhowto:kopka}
M. R. Palattella et al, \emph{Traffic Aware Scheduling Algorithm for Reliable Low-Power Multi-Hop IEEE 802.15.4e Networks} \hskip 1em plus
  0.5em minus 0.4em\relax  IEEE 23rd International Symposium on Personal, Indoor and Mobile Radio Communications - (PIMRC),  September 2012.
 
\bibitem{IEEEhowto:kopka}
N. Accettura et al, \emph{Decentralized Traffic Aware Scheduling for Multi-hop Low Power Lossy Networks in the Internet of Things} \hskip 1em plus
  0.5em minus 0.4em\relax   In World of Wireless, Mobile and Multimedia Networks (WoWMoM), 2013 IEEE 14th International Symposium and Workshops on a (pp. 1-6). IEEE,  June 2013.
 
\bibitem{IEEEhowto:kopka}
S. Duquennoy et al, \emph{Orchestra: Robust Mesh Networks Through Autonomously Scheduled TSCH} \hskip 1em plus
  0.5em minus 0.4em\relax  Proceedings of the 13th ACM Conference on Embedded Networked Sensor Systems (pp. 337-350). ACM, November 2015.

\bibitem{IEEEhowto:kopka}
K. Muraoka et al, \emph{Simple Distributed Scheduling With Collision Detection in TSCH Networks} \hskip 1em plus
  0.5em minus 0.4em\relax  IEEE Sensors Journal, 16(15), 5848-5849,  May 2016.
  
\bibitem{IEEEhowto:kopka}
L. Lamport, \emph{Time, clocks, and the ordering of events in a distributed system} \hskip 1em plus
  0.5em minus 0.4em\relax  Communications of the ACM, 21(7), 558-565, July 1978.
  
\bibitem{IEEEhowto:kopka}
T. P. Duy , \emph{Distributed cell selection for scheduling function in 6TiSCH networks} \hskip 1em plus
0.5em minus 0.4em\relax Computer Standards and Interfaces, 53, 80-88, March 2017.

\end{thebibliography}

\medskip



\end{document}
